A properly labelled proof system for intuitionistic modal logics

### 2019-09-24 caleidoscope/caleidoscope.tex
working on cut section

%%% General
\input{macros}
\input{kax_macros}
%\newcommand{\B}{\Digamma}
\newcommand{\B}{\mathcal{R}}
%\newcommand{\B}{\Xi}
%\newcommand{\B}{\mathcal{B}}
\newcommand*{\A}{\mathcal{A}}

@@

Since their introduction in the 1980s by Gabbay~\cite{gabbay:96},
\emph{labelled proof calculi} have been widely used by proof theorist
to give sound, complete and cut-free deductive system to a broad range
of logics. Unlike so-called \emph{internal calculi}, like
hyper-sequents~\cite{avron:elc96} or nested
sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09} or 2-sequents~\cite{masini:apal92},
labelled calculi have the advantage of beeing more uniform and
accommodating more logics.

@@

@@

For proving this theorem, we need a series of auxiliary lemmas.

\todo{move lemma \ref{lem:inv}}

\begin{proof}[Proof of Theorem~\ref{thm:mon-adm}]
	\todo{}
\end{proof}

@@

\begin{proof}[Proof of \ref{ii} $\rightarrow$ \ref{iii}]

>>>>

%%% General
\input{macros}
\newcommand{\B}{\mathcal{R}}
\newcommand*{\A}{\mathcal{A}}

@@

Since their introduction in the 1980s by Gabbay~\cite{gabbay:96},
\emph{labelled proof calculi} have been widely used by proof theorist
to give sound, complete and cut-free deductive system to a broad range
of logics. Unlike so-called \emph{internal calculi}, like
hyper-sequents~\cite{avron:elc96} or nested
sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09} or 2-sequents~\cite{masini:apal92},
labelled calculi have the advantage of being more uniform and
accommodating more logics.

@@

\todo{I do not know how to organize this section. First cut elimination proof? (lemma before or after?) Then mon is admissible using cut proof?}

Following the proof for the Theorem \ref{thm:cutfree-compl}, in this section, we prove the implication \ref{ii}$\implies$\ref{iii}, i.e, we want to prove that our system $\labIKp$ is complete without the \rn{cut} rule.

For proving this theorem, we need a series of auxiliary lemmas (see Lemma \ref{lem:inv}).

\begin{proof}

@@

\begin{proof}[Proof of Theorem~\ref{thm:mon-adm}]

	\todo{say that we can obtain the proof for monotonicity using the proof of cut.}

@@
